A Fast Unified Model for Parsing and Sentence Understanding

### 2016-03-18 writing/hard_stack_paper/paper.tex
Add a true t=0 step to the thin_stack fig.

\begin{table}[t]
\centering
\begin{tabular}{c|cl}
  \toprule
  $t$ & $S$[$t$] & $Q_t$ \\
  \midrule
  0 & $a$ & \underline{\hphantom{0} 0} \\
  1 & $b$ & \hphantom{0} \underline{0 1} \\
  2 & $c$ & \hphantom{0} 0 \underline{1 2} \\
  3 & $(c~b)$ & \hphantom{0} \underline{0 3} \\
  4 & $((c~b)~a)$ & \underline{\hphantom{0} 4} \\
  \bottomrule
\end{tabular}
\caption{An example of the thin-stack algorithm computing a \shift-\shift-\shift-\reduce-\reduce\ sequence on the input sentence $(a, b, c)$. $S$ is shown in the second column and may be thought of as a list of the tops of the stack at all timesteps $t$. The last two elements of $Q$ (underlined) specify which rows $t$ would be involved in a \reduce\ operation at the next timestep.}
\label{tbl:thin-stack}
\end{table}

>>>>

\begin{table}[t]
\centering
\begin{tabular}{c|cl}
  \toprule
  $t$ & $S$[$t$] & \multicolumn{1}{c}{$Q_t$} \\
  \midrule
  0 & & \underline{\hphantom{0} \hphantom{0}} \\
  1 & $a$ & \hphantom{0} \underline{\hphantom{0} 1} \\
  2 & $b$ & \hphantom{0} \hphantom{0} \underline{1 2} \\
  3 & $c$ & \hphantom{0} \hphantom{0} 1 \underline{2 3} \\
  4 & $(c~b)$ & \hphantom{0} \hphantom{0} \underline{1 4} \\
  5 & $((c~b)~a)$ & \hphantom{0} \underline{\hphantom{0} 5} \\
  \bottomrule
\end{tabular}
\caption{The thin-stack algorithm computing a \shift-\shift-\shift-\reduce-\reduce\ sequence on the input sentence $(a, b, c)$. $S$ is shown in the second column and represents the top of the stack at each step $t$. The last two elements of $Q$ (underlined) specify which rows $t$ would be involved in a \reduce\ operation at the next step.}
\label{tbl:thin-stack}
\end{table}
